---
title: "Excercises on medium extraction on a 96-well plates"
output: 
  ioslides_presentation: 
    widescreen: yes
css: theme.css
---


```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(readODS)
library(reshape2)
library(ggplot2)
library(ggbeeswarm)
library(broom)

opts_chunk$set(echo = FALSE, fig.width = 9.5)

source("./functions/read_CV.R")

# JAREK - fix me
if(Sys.info()[["nodename"]]=="MSI-GE60-2PE") {
  seq_path <- "/home/jarek/Dropbox/amyloidy/BTU_Senftenberg/BTU_2018_AL-DK-JS"
}

# JAREK - fix me
if(Sys.info()[["nodename"]] == "amyloid") {
  dat_path <- "/home/michal/Dropbox/dropbox-amylogram/BTU_Senftenberg/BTU_2018_AL-DK-JS/CrystalViolet/"
}

cv2018 <- read_cv(dat_path, "./CrystalViolet-scheme/")

no_neg_cv2018 <- filter(cv2018, medium != "NEG")

get_last_character <- function(x) {
  len_x <- nchar(x)
  substr(x, len_x, len_x)
}

cv2017 <- read.csv2("data/cv_and_videoscan.csv") %>% 
  mutate(strain = factor(strain)) %>% 
  melt(variable.name = "experiment") %>% 
  mutate(method = ifelse(grepl("CV", experiment), "CV", "Videoscan"),
         replicate = paste0("R", get_last_character(as.character(experiment))),
         medium = substr(experiment, 0, 3)) %>% 
  filter(method == "CV") %>% 
  mutate(experimentator = "JuS",
         medium = "LB",
         exp_date = "2017") %>% 
  select(strain, medium, experimentator, replicate, value, exp_date) %>% 
  filter(strain %in% unique(cv2018[["strain"]]))
  

both_measurements <- bind_rows(no_neg_cv2018, cv2017) %>% 
  filter(medium == "LB") 


```

## Overview

Created: 2018-08-04.

Parsed: `r Sys.Date()`.

## Aim 

Repeat experiments from Schiebel et al. (2017).

- Crystal Violet
- VideoScan

Learn how to extract medium solution in order to lose as few bacteria as possible.
Developing a reproducible extraction method.

## Materials

Strains used:

- 5270
- 5271
- 5272
- 5275
- 5276

The selected strains were used because they formed the strongest biofilms. 

## Methods

We compare results computing the correlation coefficient between results from Schiebel et al. (2017) and new measurements from 2018. Results are annotated as **R2017** and **R2018** respectively. 

In the case of a perfect reproduction of an experiment, the correlation coefficient should be 1. If both experiments are giving different results, the correlation coefficient is 0.

To account for normalization and baselining, we are using Spearman's correlation coefficient which relies on ranks instead of raw values.

## Crystal Violet (CV)

```{r}
ggplot(no_neg_cv2018, aes(x = strain, y = value, color = experimentator)) +
  geom_boxplot() +
  facet_wrap(~ medium) +
  theme_bw()
```


## Crystal Violet (CV)

```{r}
ggplot(no_neg_cv2018, aes(x = strain, y = value, color = experimentator)) +
  geom_quasirandom() +
  facet_wrap(~ medium) +
  theme_bw()
```


## Crystal Violet (CV)

```{r}
ggplot(both_measurements, aes(x = experimentator, y = value)) +
  geom_boxplot() +
  facet_wrap(~ strain) +
  theme_bw()
```

JuS: Jule Schiebel

## Crystal Violet (CV)

```{r}
ggplot(both_measurements, aes(x = experimentator, y = value)) +
  geom_quasirandom() +
  facet_wrap(~ strain) +
  theme_bw()
```

JuS: Jule Schiebel

## CV: medians

```{r}
agg_cv <- group_by(both_measurements, strain, experimentator, replicate) %>% 
  summarise(value = median(value)) %>% 
  summarise(value = median(value)) %>% 
  group_by(experimentator) %>% 
  mutate(value_rank = rank(value))

ggplot(agg_cv, aes(x = experimentator, y = value)) +
  geom_point() +
  facet_wrap(~ strain) +
  theme_bw()
```

JuS: Jule Schiebel

## CV: correlations

```{r}
 
cor_cv <- filter(agg_cv, experimentator == "JuS") %>% 
  ungroup() %>% 
  select(strain, proper_rank = value_rank, proper_value = value) %>% 
  inner_join(agg_cv, by = c("strain" = "strain")) %>% 
  filter(experimentator != "JuS") 

ggplot(cor_cv, aes(x = value_rank, y = proper_rank, color = strain)) +
  geom_point(size = 4) +
  geom_abline(slope = 1, intercept = 0) +
  facet_wrap(~ experimentator) +
  theme_bw()

```

## CV: correlations

```{r}
 
group_by(cor_cv, experimentator) %>% 
  do(tidy(cor.test(.[["proper_rank"]], .[["value_rank"]], method = "spearman"))) %>% 
  kable

```
